 Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation

### 2021-05-31 analysis/paper/shceof.Rmd
Corrige formato de un comentario

The large-scale extratropical circulation in the Southern Hemisphere is strongly zonally symmetric, but its zonal departures are highly relevant for surface impacts and could be related to high-impact climate extremes.
Zonal asymmetries of extratropical circulation in the Southern Hemisphere strongly modulate weather systems and regional cli8 mate through latitudinal transport of heat, humidity, and momentum [@trenberth1980].

@@

## cEOFs relationship with other variables (Quedo medio rara la divsión con los títulos. Me parece que convendrá discutir primero la relación con otros modos de circulación conocidos (SAM, Ozono) y después con las otras variables(Temp, TOC, SST, precip) )

>>>>

The large-scale extratropical circulation in the Southern Hemisphere is strongly zonally symmetric, but its zonal departures are highly relevant for surface impacts and could be related to high-impact climate extremes.
Zonal asymmetries of extratropical circulation in the Southern Hemisphere strongly modulate weather systems and regional climate through latitudinal transport of heat, humidity, and momentum [@trenberth1980].

@@

## cEOFs relationship with other variables

\textcolor{red}{Quedo medio rara la divsión con los títulos. Me parece que convendrá discutir primero la relación con otros modos de circulación conocidos (SAM, Ozono) y después con las otras variables(Temp, TOC, SST, precip)}
